---
title: "Final Project Part 1: Data Collection"
output: html_notebook
---

Scrap the list of S&P 500 and CSI 300 from Wiki.
```{r}
source("utilities.r")
# sp_500 <- scrap_index_components("GICS")
# csi_300 <- scrap_index_components("CSI")
# write.csv(csi_300,"data/csi_list.csv")
# write.csv(sp_500,"data/gics_list.csv")
sp_500 <- read.csv("data/gics_list.csv")[,-1]
# csi_300 <- read.csv("data/csi_list.csv")[,-1]
# colnames(csi_300) <- c("Index","Company","Stock.exchange","Weights","Segment")
```


Plot the frequencies of each sector.
For GICS:
```{r}
sp_500_counts <- sp_500 %>% group_by(Sector)
sp_500_counts <- sp_500_counts %>% summarise("Counts"=n())
ggplot(sp_500_counts, aes(x="", y=Counts, fill=Sector)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0)+theme_void()+ggtitle("S&P 500 Companies Sectors")
# ggsave("plot/GICS_Sectors.jpeg")
```



Stock Selection. We are not focus on quantitative stocks picking. So we choose the stocks from each industry proportionally. 

For US Portfolio:
IT, COMM: AAPL, MSFT, GOOG, FB, AMZN
CS: WMT
FIN: JPM, BAC
Industrials: BA
Healthcare: JNJ
Bonds:
TLT, LQD, HYG

Collecting US data rom Yahoo.
```{r}
US_tickers <- c("^GSPC","AAPL","MSFT","GOOG","GS","AMZN","WMT","JPM","BAC","JNJ","BA")
US_result <- collect_data(US_tickers,start_date = "2010-04-21")
CH_tickers <- c("000300.SS","600837.SS","000002.SZ","000651.SZ","000725.SZ","600036.SS","600276.SS","600887.SS","600900.SS","601318.SS","601668.SS")
CH_result <- collect_data(CH_tickers,start_date = "2010-04-21")
```

Rename and Save to csv. 
```{r}
CH_returns <- CH_result$return_data
US_returns <- US_result$return_data
 # c("000300.SS","600837.SS","000002.SZ","000651.SZ","000725.SZ","600036.SS","600276.SS","600887.SS","600900.SS","601318.SS","601668.SS")
colnames(CH_returns) <- c("CSI","Haitong","VanKe","Gree","BOE","MerchantBanks","HengRui","YiLi","YangtZe","PingAn","CSCE")
CH_returns <- na.omit(CH_returns)
```

Save files.
```{r}
write.csv(data.frame(date = index(CH_returns),coredata(CH_returns)),file = "data/CH_returns.csv")
write.csv(data.frame(date = index(US_returns),coredata(US_returns)),file = "data/US_returns.csv")
```

Try loading the files.
```{r}
CH_returns <- load_csv_xts("data/CH_returns.csv")
US_returns <- load_csv_xts("data/US_returns.csv")
```

Devide the data into research used and backtesting used.
```{r}
length(CH_returns)
nrow(CH_returns)
tail(CH_returns)
```









