---
title: "Second Part of Advanced Portfolio Management Project -- Walking Forward Portfolio Building"
output: html_notebook
author: "Kaiyi Li"
---

This part of the project aimed to build a efficient frontier based on previous data.
## Load data and functions.
```{r}
source("helper.R")
tickers <- c("SPY","TLT","HYG","LQD","GLD","BNO","VIXY")
start_date <- "2011-03-11"
num_of_tickers <- length(tickers)
result <- collect_data(tickers,start_date)
close_data <- result$close_data
return_data <- result$return_data
```

## Walkforward Optimization
```{r}
# portf<- construct_portfolio(return_data = return_data,short = F,risk_measure = "CVaR")
# portf<- construct_portfolio(return_data = return_data,short = T,risk_measure = "StdDev")
portf<- construct_portfolio(return_data = return_data,short = T,risk_measure = "CVaR")
rp <- random_portfolios(portf,1000,"sample")
opt_rebalance <- optimize.portfolio.rebalancing(
  R = return_data,
  portf,
  optimize_method = "ROI",
  rp = rp,
  rebalance_on = "months",
  training_period = 5,
  rolling_window = 10
)

```


```{r}
chart.Weights(opt_rebalance, main="Rebalanced Weights Over Time")
extractWeights(opt_rebalance)
```

```{r}
# weights <- c(0.6,0.1,0.1,-0.1,-0.1,-0.1,-0.5)
portfolio_returns <- Return.portfolio(return_data,weights = extractWeights(opt_rebalance))
# portfolio_returns <- Return.portfolio(return_data,weights = weights)
rets_df <- cbind(portfolio_returns, return_data[,1:2])
charts.PerformanceSummary(rets_df, main="P/L Over Time")
```

## Portfolio Performance Analysis
The return distribution
```{r}
plot_return_distributions(portfolio_returns,column = 1,to_local = F)
```
Correlations
```{r}
chart.Correlation(na.omit(cbind(portfolio_returns,return_data)))
```

Daily VaR
```{r}
sapply(1:3,Calculate_VaR,return_data=rets_df,method = "Gaussian")
```
CVaR
```{r}
print("Portfolio CVaR")
CVaR(portfolio_returns,method = "modified")[1]
print("SPY  CVaR")
CVaR(R = return_data[,1],method = "modified")[1]
```


Compare to Benchmark (SPY)
```{r}
chart.RelativePerformance(Ra = na.omit(rets_df)[,1],Rb =na.omit(rets_df)[,2] )
```

Drawdown
```{r}
chart.Drawdown(na.omit(rets_df)[,1:2],legend.loc = "bottomleft")
```

Rolling Performance
```{r}
# chart.RollingCorrelation(Ra = na.omit(rets_df)[,1],Rb =na.omit(rets_df)[,2])
chart.RollingRegression(Ra = na.omit(rets_df)[,1],Rb =na.omit(rets_df)[,2],attribute = "Beta",width = 230)
```

Capture Ratio
```{r}
chart.CaptureRatios(Ra = na.omit(rets_df)[,1],Rb =na.omit(rets_df)[,2])
```

CAPM 
```{r}
print("alpha")
CAPM.alpha(Ra = na.omit(rets_df)[,1],Rb =na.omit(rets_df)[,2])
print("beta")
CAPM.beta(Ra = na.omit(rets_df)[,1],Rb =na.omit(rets_df)[,2])
print("Risk Premium")
CAPM.RiskPremium(Ra = na.omit(rets_df)[,1])[1]
print("Bear Beta")
CAPM.beta.bear(Ra = na.omit(rets_df)[,1],Rb =na.omit(rets_df)[,2])
print("Bull Beta")
CAPM.beta.bull(Ra = na.omit(rets_df)[,1],Rb =na.omit(rets_df)[,2])
print("Jesen's Alpha")
CAPM.jensenAlpha(Ra = na.omit(rets_df)[,1],Rb =na.omit(rets_df)[,2])
print("Annualized Excess")
Return.annualized.excess(portfolio_returns,Rb = na.omit(rets_df)[,2])[1]
```


Save the weights and Portfolio Porformance to data folder and call it a day. 
```{r}
write.csv(data.frame(date=index(portfolio_returns), coredata(portfolio_returns))
          ,file = "data/PortfolioReturns.csv")
write.csv(data.frame(date=index(extractWeights(opt_rebalance)), coredata(extractWeights(opt_rebalance)))
          ,file = "data/PortfolioWeights.csv")
```







