---
title: "Macro Fund Project 1.1 Part d: Analysis of Economic Factors"
output: html_notebook
---
Load All Data.
```{r}
source("utilities.r")
research_data <- load_csv_xts("data/research_set.csv")
macro_economic_factors <- load_csv_xts("data/macro_factors.csv")
US_returns <- load_csv_xts("data/US_returns.csv")
macro_economic_factors <- diff(log(macro_economic_factors))
macro_research <- na.omit(merge.xts(research_data,macro_economic_factors))
# macro_research <- na.omit(merge.xts(US_returns,macro_economic_factors))
```

Let's do the regression analysis.
```{r}
colnames(macro_research)
macro_research <- na.omit(macro_research)
macro_research <- macro_research[!is.infinite(rowSums(macro_research)),]
model <- lm(macro_research$SPY~macro_research$OAS+macro_research$TED+macro_research$TreasurySpread)
summary(model)
```
```{r}
results <- c()
for (i in 1:13) {
  result <- rolling_regress(macro_research,i,to_local = T)
  r_square_result <- rolling_regress_r_square(macro_research,i,to_local = T)
  print(colnames(macro_research)[i])
  results <- cbind(result)
  print(summary(result))
}
```


Our View:

Most of stocks are too exposed to OAS, we should hedge against the business cycle. 

We need to know what is the next wave of business cycle coming. 

```{r}
macro_economic_factors <- load_csv_xts("data/macro_factors.csv")
autoplot(macro_economic_factors,facets=F)
```

Our view is that there is a another wave of recession at the time, and we should invest more into thoes who are negatively correlated with economy: LQD and TLT.


Write the data to the disk. 

```{r}
write.csv(data.frame(date = index(macro_research),coredata(macro_research)),"data/macro_research.csv")
macro_economic_factors <- load_csv_xts("data/macro_research.csv")
head(macro_research)
```








