---
title: "Macro Fund Project 1.1 Part c: Economic Data Collecting"
output: html_notebook
---

Load the data.
Before we Started, a lot of macro economic data are in monthly frequencies. So also get the series of monthly returns. 
```{r}
source("utilities.r")
research_daily_data <- load_csv_xts("data/research_set.csv")
# monthly_returns <- collect_monthly(colnames(research_data),start_date = "2010-04-22")
# write.csv(data.frame(date = index(monthly_returns),coredata(monthly_returns)),"data/monthly_returns.csv")
# monthly_returns <- load_csv_xts("data/monthly_returns.csv")
# Split it into research and backtest
# research_monthly_data <- head(monthly_returns,n=nrow(monthly_returns)-12)
# backtest_monthly_data <- tail(monthly_returns,n=12)
US_returns <- load_csv_xts("data/US_returns.csv")
```


ICE BofA US High Yield Index Option-Adjusted Spread.
The ICE BofAML Option-Adjusted Spreads (OASs) are the calculated spreads between a computed OAS index of all bonds in a given rating category and a spot Treasury curve. 
TED is the TED spread.

```{r}
OAS <- getSymbols("BAMLH0A0HYM2",src="FRED",auto.assign = F)
OAS <- na.omit(OAS)
OAS <- OAS[index(US_returns)]
TED <- getSymbols("TEDRATE",src="FRED",auto.assign = F)
TED <- na.omit(TED)
TED <- TED[index(US_returns)]
TreasurySpread <- getSymbols("T10Y2Y",src="FRED",auto.assign = F)
TreasurySpread <- na.omit(TreasurySpread)
TreasurySpread <- TreasurySpread[index(US_returns)]
```

```{r}
macro_economic_factors <- na.omit(merge.xts(OAS,TED,TreasurySpread))
colnames(macro_economic_factors) <- c("OAS","TED","TreasurySpread")
head(macro_economic_factors)
```

Save it to the csv.

```{r}
write.csv(data.frame(date = index(macro_economic_factors),coredata(macro_economic_factors)),"data/macro_factors.csv")
macro_economic_factors <- load_csv_xts("data/macro_factors.csv")
head(macro_economic_factors)
```







